% Group Meetings and Team Member Roles:
% How frequently and for how long do you intend to (virtually) meet?
% Please remember to time-box the meetings!
% When will you schedule the sprint retrospective meetings?
% Did you arrange for additional feedback channels with the customer (e.g., via Slack or email)?
% Please name the Scrum Masters for each sprint (each team member can only be the Scrum Master for up to one sprint)
\begin{spacing}{1.3}

\section{Group Meetings and Team Member Roles}

Stand-up meetings are currently scheduled for two meetings per week. These are to be held every Monday and Friday until the completion of the project. During the later stages of the project, once the team has settled into their roles, a third stand-up meeting may be added. These stand-up meetings are time-boxed to 15 minutes. This ensures that there is sufficient time for all team members to share their progress, intended work and blockers, whilst keeping the meeting short. Should any problems arise during the stand-up meetings, individual team members may schedule `offline' meetings to work through potential solutions. \\
\vspace{-5pt}

Client meetings, including the Sprint review and planning meetings, will be held with the tutor bi-weekly on Fridays at 1pm. The review and planning meetings will be combined to a single meeting due to the availability of contact time with the tutor (and client). This single meeting will be time-boxed to 25 minutes. \\
\vspace{-5pt}

Sprint retrospectives are usually held between the sprint review and sprint planning meetings, however due to the nature of the single review-planning meeting, this will be held at a separate time. 
This retrospective meeting will be held after the review-planning in place of the `daily' stand-up.

\subsection{Scrum Masters}

The scrum masters for each sprint are listed in Table \ref{tab:scrumMasters}.
Scrum masters were selected through self-nomination and election and assigned at random to sprints. 

\begin{table}[htbp]
    \centering
    \begin{tabular}{@{}r|l@{}}
    \toprule
        \textbf{Sprint} & \textbf{Scrum Master} \\
        \hline
        1 & Colin Ross \\
        2 & Jackson Dearing\\
        3 & Joshua Tatton\\
        4 & Elliot Wheatland\\
        5 & Steven Monger\\
        \bottomrule
    \end{tabular}
    \caption{Scrum Masters}
    \label{tab:scrumMasters}
\end{table}

\end{spacing}