% Project Vision:
% Brief (100-200 words) summary of the project vision in your own words
%%COMPLETE & REVIEWED BY KP
\section{Project Vision}
\begin{spacing}{1.3}
% I have added more backround and just trimmed the wording - KP
Propic is a company that provides analyst services for the Real Estate sector, using big data and artificial intelligence. Their business intelligence product, ReVeal AI, generates recommendations for real estate agents for listings and appraisals. Part of this development process involves analysts querying the system to facilitate answering business questions. The transformation process has been refined over time in order to facilitate answering increasingly sophisticated and abstract business questions. These refinements have introduced increased complexity, leading to difficulty in understanding, validating and risk-managing the transformation process. 

The aim of the project is to provide a visualisation tool which allows analysts to easily understand the data transformation. For each SQL script provided by a user, this tool will derive the relevant table and data lineage. The information will be displayed in a web browser in a clear and intuitive manner. Interactive elements will allow users to highlight only the data lineage information which is related to an individual table. This will enable developers and the end user to better understand why, how and where recommendations are coming from. This will enable Propic to better refine their understanding and build more reliable and explanable systems.
\end{spacing}
